Visualizing Independence Using Extended Association and Mosaic Plots

### 2004-10-26 trunk/vcd/inst/doc/dsc2003-independence.Rnw
fix for namespace, vignette, and tabplot to enable build.
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/vcd@306 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\setkeys{Gin}{width=0.7\textwidth}
\begin{figure}[htbp]
\begin{center}
<<goals-assoc-classic,fig=TRUE,echo=FALSE,height=6,width=7,results=hide>>=
grid.assocplot(goals, rot = 0, gp = gp.binary)
@
\caption{Association plot for the Bundesliga data.}
\label{fig:goals-assoc-classic}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
<<goals-mosaic-classic,fig=TRUE,echo=FALSE,height=6,width=7>>=
mosaicplot(t(goals), shade = TRUE, main = "")
@
\caption{Friendly mosaic plot for the Bundesliga data.}
\label{fig:goals-mosaic-classic}
\end{center}
\end{figure}

@@

\setkeys{Gin}{width=0.8\textwidth}
\begin{figure}[htbp]
\begin{center}
<<goals-assoc-signif,fig=TRUE,echo=FALSE,height=6,width=6>>=
grid.assocplot(goals, rot = 0)
@
\caption{Extended association plots for the Bundesliga data.}
\label{fig:goals-assoc-signif}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
<<haireye-assoc-signif,fig=TRUE,echo=FALSE,height=6,width=6>>=
grid.assocplot(haireye)
@
\caption{Extended association plots for the Hair-Eye-Color data (female students).}
\label{fig:haireye-assoc-signif}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
<<goals-mosaic-signif,fig=TRUE,echo=FALSE,height=6,width=6>>=
grid.mosaicplot(t(goals), main = NULL)
@
<<haireye-mosaic-signif,fig=TRUE,echo=FALSE,height=6,width=6>>=
grid.mosaicplot(t(haireye), main = NULL)
@
\caption{Extended mosaic plots for the Bundesliga and Hair-Eye-Color data (female students).}
\label{fig:both-mosaic-signif}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
<<UCB-mosaic-signif,fig=TRUE,echo=FALSE,height=8,width=8>>=
##grid.mosaicpairs(UCBAdmissions, type = "conditional", main = NULL)
grid.mosaicpairs(UCBAdmissions, type = "conditional", permute = FALSE)
@
\caption{Extended conditioned association plots for the UCB Admissions data.}
\label{fig:UCB-mosaic-signif}
\end{center}
\end{figure}

>>>>

\setkeys{Gin}{width=0.7\textwidth}
\begin{figure}[htbp]
\begin{center}
<<goals-assoc-classic,fig=TRUE,echo=FALSE,height=6,width=7,results=hide>>=
assoc(goals, shade = TRUE, gp = gp.binary())
@
\caption{Association plot for the Bundesliga data.}
\label{fig:goals-assoc-classic}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
<<goals-mosaic-classic,fig=TRUE,echo=FALSE,height=6,width=7>>=
mosaic(goals, shade = TRUE)
@
\caption{Friendly mosaic plot for the Bundesliga data.}
\label{fig:goals-mosaic-classic}
\end{center}
\end{figure}

@@

\setkeys{Gin}{width=0.8\textwidth}
\begin{figure}[htbp]
\begin{center}
<<goals-assoc-signif,fig=TRUE,echo=FALSE,height=6,width=6>>=
assoc(goals)
@
\caption{Extended association plots for the Bundesliga data.}
\label{fig:goals-assoc-signif}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
<<haireye-assoc-signif,fig=TRUE,echo=FALSE,height=6,width=6>>=
assoc(haireye)
@
\caption{Extended association plots for the Hair-Eye-Color data (female students).}
\label{fig:haireye-assoc-signif}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
<<goals-mosaic-signif,fig=TRUE,echo=FALSE,height=6,width=6>>=
mosaic(goals)
@
<<haireye-mosaic-signif,fig=TRUE,echo=FALSE,height=6,width=6>>=
mosaic(haireye)
@
\caption{Extended mosaic plots for the Bundesliga and Hair-Eye-Color data (female students).}
\label{fig:both-mosaic-signif}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
<<UCB-mosaic-signif,fig=TRUE,echo=FALSE,height=8,width=8>>=
##grid.mosaicpairs(UCBAdmissions, type = "conditional", main = NULL)
pairs(UCBAdmissions, type = "conditional")
@
\caption{Extended conditioned association plots for the UCB Admissions data.}
\label{fig:UCB-mosaic-signif}
\end{center}
\end{figure}
